
\documentclass[11pt]{article}
%\hyphenation{Bar-ce-lo-na}
% Font settings
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{marvosym}% provides \Letter and \Telefon
%\usepackage[cmintegrals,cmbraces]{newtxmath}
\usepackage[osf,sb]{ebgaramond}
\usepackage{enumitem}
\setitemize{nosep}
% Margins
%\usepackage[margin=1.5in]{geometry}

% Section fonts
\usepackage{titlesec}
\titleformat*{\section}{\large\scshape\bfseries\raggedright}
\titleformat*{\subsection}{\scshape\raggedright}
\titleformat*{\subsubsection}{\normalfont\normalsize\bfseries\itshape}


% Headers, footers, and page styles
\usepackage{titleps}
\newpagestyle{main}[\footnotesize]{%
  \headrule
  \sethead[Curriculum Vit\ae][][Luis Alonso-Ovalle]
          {Curriculum Vit\ae}{}{Luis Alonso-Ovalle}
            \setfoot{}{}{\scriptsize Updated \today}
}
\newpagestyle{first}[\footnotesize]{%
  \sethead{}{}{}
  \setfoot{}{}{\scriptsize \today}
}
\pagestyle{main}

\titlespacing*{\section}
{0pt}{10pt}{0pt}
\titlespacing*{\subsection}
{0pt}{10pt}{0pt}
\titlespacing*{\subsubsection}
{10pt}{15pt}{0pt}
\titlespacing*{\paragraph}
{0pt}{10pt}{0pt}



%% links
\usepackage{color}
\definecolor{RoyalBlue}{cmyk}{1.,0.50,0,0}
%\usepackage{gb4e}
\usepackage[colorlinks=true,breaklinks=true linkcolor=RoyalBlue, citecolor=RoyalBlue, urlcolor=RoyalBlue]{hyperref}


\usepackage{multicol}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}%\nonzeroparskip
 %\usepackage[colorlinks=true, breaklinks=true linkcolor=RoyalBlue, citecolor=RoyalBlue, urlcolor=RoyalBlue]{hyperref}
\usepackage{array}


\begin{document}
%\garamond
\markright{}
\thispagestyle{plain}
\author{}
\vspace{-2cm}
\begin{center}
{\LARGE Luis Alonso-Ovalle}
\end{center}

\vspace{.4cm}

\section*{Contact Information}
\begin{multicols}{2}
Department of Linguistics\\
1085 Dr. Penfield\\
Montr\'eal, Qu\'ebec, Canada, \textsc{h3a 1a7}\\
\Telefon \hspace{2pt} \href{tel:0015143984353}{(001)$\cdot$514$\cdot$398$\cdot$4353}
\\
\hspace{1pt} \FAX \hspace{1pt} (001)$\cdot$514$\cdot$398$\cdot$7088
(non-confidential) \\
\end{multicols}
\vspace{-12pt}
\Letter \hspace{3pt}  \href{mailto:luis.alonso-ovalle@mcgill.ca}{luis.alonso-ovalle@mcgill.ca}\\
\ComputerMouse \hspace{6pt}
\href{http://people.linguistics.mcgill.ca/~luis.alonso-ovalle/}{http://people.linguistics.mcgill.ca/$\sim$luis.alonso-ovalle/}

\section*{Education}

\begin{tabular}{p{2.815cm}p{280pt}}
Ph.D., 2006 &  Linguistics, University of Massachusetts at Amherst\\
 & {\footnotesize Dissertation: \textit{Disjunction in Alternative Semantics.}}\\
 &  {\footnotesize Committee: Angelika Kratzer (chair), Kai von Fintel, Lyn Frazier,
Kevin}\\
& {\footnotesize Klement (external member), Barbara H. Partee, Christopher Potts.}\\
% \item[Spring 2001.] Doctoral candidate (\textsc{a.b.d.}), 
% Department of Spanish and Portuguese, University of Massachusetts,
% Amherst (Major: Syntax and Semantics. Minor: General Linguistics.)
&  \\[-8pt]
M.A., 2001   & Hispanic Linguistics, University of Massachusetts at Amherst\\
 &  \\[-8pt]
\textit{Licenciatura}, 1997  & Hispanic Philology,  University of Oviedo, Spain\\
 %& & {\footnotesize First Class Honors (`Clar\'in Award')}\\
\end{tabular}

\section*{Professional Experience}

\begin{tabular}{p{2.815cm}p{280pt}}
August 2016 -- &  Chair, Department of Linguistics\\
 May 2022 &McGill University\\
 & \\[-8pt]
August 2015 -- & Associate Professor, Department of Linguistics\\
 & McGill University\\
  & \\[-8pt]
June 2014 -- &  Associate Professor\\
July 2015 & Department of Linguistics and Department of Languages, Literatures, and Cultures\\ 
& McGill University\\
& \\[-8pt]
August 2011 -- &  Assistant Professor\\
May 2014& Department of Linguistics and Department of Languages, Literatures, and Cultures\\ 
& McGill University\\
& \\[-8pt]
\end{tabular}
\begin{tabular}{p{2.815cm}p{280pt}}
Sept. 2006 -- & Assistant Professor\\
May 2011&   Department of
Hispanic Studies\\
&  University of Massachusetts, Boston\\
 &  \footnotesize{[Spring 2010: parental leave.]}\\
& \\[-8pt]
Fall 2005 & Lecturer \\
& Department of Linguistics and Philosophy \\ 
& Massachusetts Institute of Technology\\
& \\[-8pt]
\end{tabular}
\begin{tabular}{p{2.815cm}p{280pt}}
Fall 2003 -- & Teaching Assistant\\
 Spring 2004&  Department of
Linguistics\\
& University of Massachusetts at Amherst\\ 
& \\[-9pt]
% Department of Linguistics, University of Massachusetts, Amherst. 
% \textsc{Ling 510:} Introduction to Semantics. Level: senior-level undergraduate course. Duties included preparing and teaching a weekly 50 min. hands-on session, supervising students and grading.
Spring 2001 -- & Research Assistant\\
 Fall 2003 &  Department of Linguistics and Department of Psychology\\
&  University of Massachusetts at Amherst\\
 & \\[-8pt]
1997 --&  Teaching Associate\\
 2000 &  Department of Spanish and Portuguese\\
&  University of Massachusetts at Amherst\\
&  \\[-8pt]
% Full responsibility for all aspects of the following courses, including student evaluation: \textsc{span 470}: Introduction to Hispanic Linguistics; \textsc{span 378}: Spanish Phonetics; \textsc{span 311}: Advanced Grammar, \textsc{span 240}: Spanish for General Purposes, Advanced Intermediate level; \textsc{span 120}:  Spanish for General Purposes, Beginners; \textsc{span 110}: Spanish for General Purposes, Beginners.
 1998 -- & Coordinator, Advanced Intermediate Level
 Language  Program\\
 2000& Department of Spanish and Portuguese \\
 &  University of Massachusetts at Amherst\\
 &  \\[-8pt]
% Duties included coordinating Teaching Associates in charge of \textsc{span} 240 (Spanish for General Purposes, Advanced Intermediate level), designing full structure of the course, including syllabus, teaching materials and evaluation of students.
Fall 1999 & Teaching Assistant\\
 & Spanish Department, Amherst
College\\
 & \\[-8pt]
Summer 1996  & Institute for the Cooperation with Latin America
Fellow\\
 & Ministry of Foreign Affairs, Spain\\
\end{tabular}



\section*{Research}

\subsection*{Grants}

\textit{Principal Investigator:}

 Social Sciences and Humanities Research
Council of Canada, Insight Grant, \textit{Modality across Categories: Modal Indefinites and the Projection of Possibilities} (435-2018-0524), (2018-2022), \$242,686. (Co-investigators:
Bernhard Schwarz, Junko Shimoyama.)

 Social Sciences and Humanities Research
Council of Canada, Insight Grant, \textit{Modality in the Nominal
  Domain} (435-2013-0103), (2013-2017), \$278,758. (Co-investigators:
Bernhard Schwarz, Junko Shimoyama.)

Fonds Qu\'eb\'ecois de la Recherche sur la
Societ\'e et la Culture, \'Etablissement de
nouveaux professeurs-chercheurs, \textit{Variations
  entre langues dans la s\'emantique des groupes nominaux ind\'efinis:
  l'expression de l'ignorance et de l'indifference} (2013-NP-164823),
(2012-2015), \$39,600.


\textit{Co-Applicant:} 

Fonds Qu\'eb\'ecois de la Recherche sur la
Societ\'e et la Culture, Soutien aux \'equipes de recherche,
\textit{Les interfaces de la syntaxe}, (2012-2015), \$344,693 (Lisa
Travis, PI).

\textit{Dissemination:}

Principal Applicant: Social Sciences and Humanities Research Council
of Canada, Connection Grant, \textit{Exploring the Interfaces:
  Implicatures, Alternatives and the Semantics/Pragmatics Interface}
(611-2012-0232), \$16,342. (Funding for a three-day international workshop.)


%Department of Hispanic Studies, travel grants: summer 2007 \$800,
%summer 2008 \$600.

\textit{Previous Internal Grants:}

College of Liberal Arts Dean's Research Fund (Spring 2008) ``Spanish Epistemic Indefinites'', \$3,000, plus one course release.

Joseph P. Healey Grant Program (AY 2008-2009), Office of the
  Vice Provost for Research, University of Massachusetts Boston: ``The
  Place of Spanish Indefinites within a Typology of Epistemic
  Indefinite Noun Phrases: Stage 2'', \$4,410.

Joseph P. Healey Grant Program (AY 2007-2009), Office of the Vice Provost for Research, University of Massachusetts Boston: ``The Place of Spanish Indefinites within a Typology of Epistemic Indefinite Noun Phrases'', \$3,890.


\subsection*{Journal Articles}


Alonso-Ovalle, Luis \textit{\&} Vincent Rouillard. (forthcoming) Spanish Bare Interrogatives and Number, \textit{Journal of Semantics}.


Alonso-Ovalle, Luis \textit{\&} Elizabeth Heredia-Murillo. (2023) Concessive Scalar Particles:
Symmetric vs. Non-Symmetric Alternatives.
The Case of Spanish \textit{Siquiera}, \textit{Glossa: A Journal of General Linguistics}, 8(1). \href{https://doi.org/10.16995/glossa.8574}{https://doi.org/10.16995/glossa.8574}

 
Alonso-Ovalle, Luis \textit{\&} Aron Hirsch. 2022. Keep \textit{Only} Strong,  \textit{Semantics and Pragmatics}, 15(6). \href{https://doi.org/10.3765/sp.15.6}{https://doi.org/10.3765/sp.15.6}
%Full DOI: https://doi.org/10.3765/sp.15.6
%Short DOI: https://doi.org/h2wp

Alonso-Ovalle, Luis \textit{\&} Justin Royer. 2021. Random Choice from Likelihood: The Case of Chuj (Mayan), \textit{Journal of Semantics}, 38(4), 483-529. 
%\\ \hspace*{\hfill}(\href{https://doi.org/10.1093/jos/ffab009}{https://doi.org/10.1093/jos/ffab009})

%Journal of Semantics, Volume 38, Issue 4, November 2021, Pages 483–529, https://doi.org/10.1093/jos/ffab009

Alonso-Ovalle, Luis \textit{\&} Henrison Hsieh. 2021. Causes and Expectations: On the Interpretation of the Tagalog Ability / Involuntary Action form, \textit{Journal of Semantics}, 38(3), 441-472.% \hspace*{\hfill} (\href{https://doi.org/10.1093/jos/ffab008}{https://doi.org/10.1093/jos/ffab008}).

Alonso-Ovalle, Luis \textit{\&} Paula Men\'endez-Benito. 2018. Projecting Possibilities in the Nominal Domain. Spanish \textit{Uno Cualquiera}, \textit{Journal of Semantics}. 35:1, 1-41. %\\
%\hspace*{\hfill}(\href{https://doi.org/10.1093/jos/ffx011}{https://doi.org/10.1093/jos/ffx011})

%[Accepted Dec 2016]

Alonso-Ovalle, Luis \textit{\&} Paula
    Men\'endez-Benito. 2013. Two Views on Epistemic
    Indefinites. \textit{Language and Linguistics Compass}, 7:2, 102-122. 

Alonso-Ovalle, Luis \textit{\&} Paula
    Men\'endez-Benito.\ 2012. Indefinites, Dependent Plurality, and
    the Viability Requirement on Scalar Alternatives. \textit{Journal
      of Semantics}. 30:1. 65-102. %Published online on February 20 2012. doi: 10.1093/jos/ffr013

Alonso-Ovalle, Luis \textit{\&} Paula
    Men\'endez-Benito.\ 2011.\ Domain Restrictions, Modal
    Implicatures, and Plurality: Spanish \textit{Algunos.}
    \textit{Journal of Semantics}, 28 (2): 211-240.


Alonso-Ovalle, Luis \textit{\&} Paula
    Men\'endez-Benito. 2010. Modal Indefinites. \textit{Natural
      Language Semantics} 18 (1): 1-31. 
% \begin{itemize}[ ]
% \item Preprint {\scshape url:} \href{http://www.alonso-ovalle.net/wp-content/uploads/modal-indefinites.pdf}{www.alonso-ovalle.net/wp-content/uploads/modal-indefinites.pdf}
% \end{itemize}

Alonso-Ovalle, Luis. 2009. Counterfactuals,
  Correlatives and Disjunction. \textit{Linguistics and Philosophy} 32 (2): 207-244.
% \begin{itemize}[ ]
% \item DOI: 10.1007/s10988-009-9059-0
% \item Preprint {\scshape url:} \href{http://www.alonso-ovalle.net/wp-content/uploads/conditionals.pdf}{www.alonso-ovalle.net/wp-content/uploads/exclusive-or.pdf}
% \end{itemize}


Christopher Potts, Luis Alonso-Ovalle, Ash Asudeh,
    Rajesh Bhatt, Seth Cable, Christopher Davis, Yurie Hara, Angelika
    Kratzer, Eric McCready, Tom Roeper, and Martin Walkow. 2009. 
  Expressives and Identity Conditions. \textit{Linguistic Inquiry}, 40
  (2) : 356-366. [Squib]

Alonso-Ovalle, Luis. 2008a. Innocent Exclusion in an
  Alternative Semantics. \textit{Natural Language Semantics} 16 (2):
  115-128. 

% \begin{itemize}[ ]
% \item DOI: 10.1007/s11050-008-9027-1
% \item Preprint {\scshape url:} \href{http://www.alonso-ovalle.net/wp-content/uploads/exclusive-or.pdf}{www.alonso-ovalle.net/wp-content/uploads/exclusive-or.pdf}
% \end{itemize}

Alonso-Ovalle, Luis; Charles Clifton; Susana Fern\'andez-Solera \textit{\&} Lyn Frazier. 2002. Null \textit{vs.} Overt Pronouns and the Topic-Focus Articulation in Spanish, \textit{Journal of Italian Linguistics}, 14:2, pp. 151-169. 
% \begin{itemize}[ ]
% \item Preprint {\scshape url:} \href{http://www.alonso-ovalle.net/tfa.pdf}{www.alonso-ovalle.net/papers/tfa.pdf}
% \end{itemize}

Alonso-Ovalle, Luis. 2000. Aspectos gnoseol\'ogicos de la ling\"u\'istica de Cuervo. \textit{Thesaurus}, LXIII, Instituto Caro y Cuervo, Bogot\'a (Colombia), pp. 345-378. 
% \begin{itemize}[ ]
% \item Offprint {\scshape url:} \href{http://www.alonso-ovalle.net/papers/Cuervo-Thesaurus.pdf}{www.alonso-ovalle.net/papers/Cuervo-Thesaurus.pdf}
% \end{itemize}


% \end{revnumerate}

\subsection*{Book chapters} 
% \renewcommand{\labelenumi}{{A}\theenumi.}
% \renewcommand{\theenumii}{\roman{\enumii}}
% \begin{revnumerate}

Alonso-Ovalle, Luis \textit{\&} Paula Men\'endez-Benito. 2020. Free Choice Items and Modal Indefinites. \textit{The Wiley Blackwell Companion to Semantics}, ed. by Lisa Matthewson, Cecile Meier, Hotze Rullmann, and Thomas E. Zimmerman, Wiley Blackwell, 39 pages. %doi: 10.1002/9781118788516.sem00

Alonso-Ovalle, Luis \textit{\&} Paula Men\'endez-Benito. 2017. Epistemic Indefinites: On the Content and Distribution of the Epistemic Effect. \textit{Modality across Syntactic Categories.} ed. by Ana Arregui, Marisa Rivero, and Andr\'es Pablo Salanova, Oxford University Press, pp. 11-30.

Alonso-Ovalle, Luis \textit{\&} Junko Shimoyama. 2017. Modal Indefinites: Where do Japanese \textit{Wh-ka}s Fit In? \textit{Modality across Syntactic Categories} ed. by Ana Arregui, Marisa Rivero, and Andr\'es Pablo Salanova, Oxford University Press,  pp. 30-49.

Alonso-Ovalle, Luis \textit{\&} Paula Men\'endez-Benito. 2015. Epistemic Indefinites: An Overview. \textit{Epistemic Indefinites. Exploring Modality beyond the Verbal Domain}, ed.\ by Luis Alonso-Ovalle \& Paula Men\'endez-Benito, Oxford University Press, pp. 1-28.

Alonso-Ovalle, Luis \textit{\&} Paula Men\'endez-Benito. 2013. A Note on the Derivation of the Epistemic Effect of Spanish
\textit{Alg\'un} as an Implicature. \textit{Alternatives in Semantics}, ed. by
Anamaria F\u{a}l\u{a}u\c{s}, Palgrave McMillan (\textit{Palgrave
  Studies in Pragmatics, Language and Cognition Series}), pp. 36-50.

Alonso-Ovalle, Luis \textit{\&} Paula Men\'endez-Benito. 2013. Exceptional Scope: The Case of Spanish. \textit{Different Kinds of Specificity Across Languages}, ed. by
Stefan Hinterwimmer and Cornelia Endriss, Dordrecht: Springer
(\textit{Studies in Linguistics and Philosophy}), pp. 123-155.

Alonso-Ovalle, Luis. 2003. Incremental Modification of Discourse Referents: the Case of Restricted Quantification. \textit{On Semantic Processing, University of Massachusetts Occasional Papers in Linguistics (\textsc{umop}) vol. 27}, ed. by Luis Alonso-Ovalle, Amherst, MA: Graduate Linguistic Student Association, pp. 1-26.
%  \begin{itemize}[ ]
% \item Preprint {\scshape url:} \href{http://www.alonso-ovalle.net/papers/incremental.pdf}{www.alonso-ovalle.net/papers/incremental.pdf}
%  \end{itemize}

Alonso-Ovalle, Luis. 2003. Spanish {\it De-}Clauses are not Always in the Right Mood. {\it Romance Linguistics and Linguistic Theory 2001}, ed. by Josep Quer, Jan Schroten, Mauro Scorretti, Petra Sleeman and Els Verheugd, Amsterdam: John Benjamins, pp. 1-16. 
% \begin{itemize}[ ]
% \item Preprint {\scshape url:} \href{http://www.alonso-ovalle.net/papers/gr01.pdf}{www.alonso-ovalle.net/papers/gr01.pdf}
% \end{itemize}

Alonso-Ovalle, Luis. 2002. Arbitrary Pronouns are not that Indefinite.  {\it Romance Languages and Linguistic Theory 2000,} ed.\ by Claire Beyssade, Reineke Bok-Bennema, Frank Drijkoningen and Paola Monachesi, Amsterdam: John Benjamins, pp. 1-15. 
% \begin{itemize}[ ]
% \item Preprint {\scshape url:} \href{http://www.alonso-ovalle.net/papers/Utrecht.pdf}{www.alonso-ovalle.net/papers/Utrecht.pdf}
% \end{itemize}

Alonso-Ovalle, Luis. 2002. Aspect and Situations: A Situation Semantics Account of the Semantic Variability of Spanish `\emph{Al}-Clauses'. \textit{From Words to Discourse. Trends in Spanish Semantics and Pragmatics.} ed. by Javier Guti\'errez-Rexach. Oxford/New York: Elsevier Science, pp. 119-127. 
% \begin{itemize}[ ]
% \item Preprint {\scshape url:} \href{http://www.alonso-ovalle.net/papers/AspectandSituations99.pdf}{www.alonso-ovalle.net/papers/AspectSituations99.pdf}
% \end{itemize}

Alonso-Ovalle, Luis \textit{\&} Francesco D'Introno. 2001. Full and Null Pronouns in Spanish: the Zero Pronoun Hypothesis. \textit{Hispanic Linguistics at the Turn of the Myllenium,} ed. by H\'ector Campos, Elena Herburger, Alfonso Morales-Front, and Thomas Walsh, Somerville, MA: Cascadilla Press, pp. 189-210.
% \begin{itemize}[ ]
% \item Preprint {\scshape url:} \href{http://www.alonso-ovalle.net/papers/Pronouns.pdf}{www.alonso-ovalle.net/papers/Pronouns.pdf}
% \end{itemize}

Alonso-Ovalle, Luis. 2000. Is the `Arbitrary Interpretation' a Semantic Epiphenomenon? {\it Issues in Semantics and its Interface, University of Massachusetts Occasional Papers in Linguistics (\textsc{umop}) vol. 2}, ed. by  Niyomi Kusumoto and Elisabeth Villalta, Amherst, MA: Graduate Linguistic Student Association , pp. 155-183. 
% \begin{itemize}[ ]
% \item Preprint {\scshape url:} \href{http://www.alonso-ovalle.net/papers/ArbReferenceFinal.pdf}{www.alonso-ovalle.net/papers/ArbReferenceFinal.pdf}
% \end{itemize}


% \end{revnumerate}

\subsection*{Proceedings Papers}

Alonso-Ovalle, Luis and Esmail Moghiseh. 2022. Universal Force from Exhaustification: Farsi \textit{Hame -i} DPs, \textit{Proceedings of the Thirty-Second Semantics and Linguistic Theory Conference}, ed. by John R. Starr, Juhyae Kim and Burak \"{O}ney, CLC Publications, Cornell University, pp. 619-638. %\\ \hspace*{\fill} \href{https://doi.org/10.3765/salt.v1i0.5401}{https://doi.org/10.3765/salt.v1i0.5401}


Alonso-Ovalle, Luis and Esmail Moghiseh. 2022. Farsi \textit{Hame -i} DPs and Intensional Transitive Verbs, \textit{Proceedings of the 23rd Amsterdam Colloquium}, ed. by Marco Degano, Tom Roberts, Giorgio Sbardolini and Marieke Schouwstra, pp 214-220.%\\ \hspace*{\fill} \href{https://events.illc.uva.nl/AC/AC2022/Proceedings/}{https://events.illc.uva.nl/AC/AC2022/Proceedings/}

Alonso-Ovalle, Luis, Paula Men\'endez-Benito and Aynat Rubinstein. 2022. Event-Dependent Modal Projection: The Case of Spanish Subjunctive Relative Clauses, \textit{Proceedings of the Fifty-Second Annual Meeting of the North East Linguistic Society}, ed. by \"{O}zge Bakay, Breanna Pratley, Eva Neu and Peyton Deal, University of Massachusetts, Amherst, MA: Graduate Linguistics Student Association, pp 15-28.

Alonso-Ovalle, Luis and Jonathan Palucci. (forthcoming) Obligatory Wide Scope for \textit{Any} DPs?, \textit{Proceedings of the Thirty-Ninth West Coast Conference on Formal Linguistics}.

Alonso-Ovalle, Luis and Justin Royer. 2021. Modality in the Nominal Domain: \textit{Yalnhej} DPs in Chuj, \textit{Proceedings of the Thirty-First Semantics and Linguistic Theory Conference}, ed. by Nicole Dreier, Chloe Kwon, Thomas Darnell, and John Starr, CLC Publications, Cornell University, pp. 061-081.

Alonso-Ovalle, Luis and Jonathan Palucci. 2021. Numeral \textit{Any}: in Favor of Viability, \textit{Proceedings of the Fifty-First Annual Meeting of the North East Linguistic Society}, ed. by Alessa Farinella and Angelica Hill, University of Massachusetts, Amherst, MA: Graduate Linguistics Student Association, pp 1-11.

 Alonso-Ovalle, Luis and Esmail Moghiseh. 2021. Numeral \textit{Any}: the View from Farsi, \textit{Proceedings of the Thirtieth Semantics and Linguistic Theory Conference}, ed. by Joseph Rhyne, Kaelyn Lamp, Nicole Dreier, and Chloe Kwon, CLC Publications, Cornell University, pp. 485-503. %{\footnotesize [\href{https://doi.org/10.3765/salt.v30i0.4829}{https://doi.org/10.3765/salt.v30i0.4829}]}
      
    Alonso-Ovalle, Luis and Justin Royer. 2020. Random choice modality: The view from Chuj (Mayan), \textit{Proceedings of the Twenty-Fourth Annual} Sinn und Bedeutung \textit{Conference}, ed. by Michael Franke, Nikola Kompa, Mingya Liu, Jutta L. Mueller, and Juliane Schwab, Osnabr\"{u}ck University, Humboldt University of Berlin, pp. 48-65. 
    %{\footnotesize [\href{https://semanticsarchive.net/Archive/mZhNDA4Y/SuB24-twovolume.pdf}{https://semanticsarchive.net/Archive/mZhNDA4Y/SuB24-twovolume.pdf}]}
    
      Alonso-Ovalle, Luis and Esmail Moghiseh. 2019. Neutralizing Free Choice Items via Maximal Domain
Restriction: Farsi \textit{-i} Indefinites, \textit{Proceedings of the Twenty-Ninth Semantics and Linguistic Theory Conference}, ed. by Katherine Blake, Forrest Davis, Kaelyn Lamp, and Joseph Rhyne, CLC Publications, pp. 686–705. 
%{\footnotesize [\href{https://doi.org/10.3765/salt.v29i0.4636}{https://doi.org/10.3765/salt.v29i0.4636}]}
      
Alonso-Ovalle, Luis, and Vincent Rouillard. 2019. Number Inflection, Spanish Bare Interrogatives, and Higher-Order Quantification. \textit{Proceedings
of the Forty-Ninth Annual Meeting of the North East Linguistic Society}, ed. by Maggie Baird and Jonathan Pesetsky, University of Massachusetts, Amherst, MA: Graduate Linguistics Student Association, pp 25-39.
 
 Alonso-Ovalle, Luis and Esmail Moghiseh. 2019. Contradiction-Free Strengthening and Alternative Discharge: The Case of Farsi \textit{-i} Indefinites. \textit{Proceedings of the Twenty-Third Annual} Sinn und Bedeutung \textit{Conference}, ed. by Mar\'ia Teresa Espinal, Elena Castoviejo, Manuel Leonetti, Louise McNally, and Cristina Real-Puigdollers, Universitat Aut\`onoma de Barcelona, Ikerbasque and UPV/EHU, Universidad de Alcal\'a and Universitat Pompeu Fabra, pp. 1-18. %{\footnotesize [\href{https://semanticsarchive.net/Archive/Tg3ZGI2M/SuB23-twovolume.pdf}{https://semanticsarchive.net/Archive/Tg3ZGI2M/SuB23-twovolume.pdf}]}
      
 Royer, Justin, and Luis Alonso-Ovalle. 2019. Randon Choice Modality in Chuj: The Case of \textit{Komon}. \textit{Proceedings of Form and Analysis in Mayan Linguistics 5 (FAMLi 5)}, ed. by Ryan Bennett, Robert Henderson, Pedro Mateo Pedro, and Megan Harve, {\footnotesize [\href{https://escholarship.org/uc/item/5587h7df}{https://escholarship.org/uc/item/5587h7df} ]}
      
Alonso-Ovalle, Luis, and Aron Hirsch. 2018. Keep \textit{Only} Strong. \textit{Proceedings of the Twenty-Eighth Semantics and Linguistic Theory Conference}, ed. by Sireemas Maspong, Brynhildur Stef\'ansd\'ottir, Katherine Blake and Forrest Davis, CLC Publications, pp. 251-270. %{\footnotesize [\href{https://doi.org/10.3765/salt.v28i0.4439}{https://doi.org/10.3765/salt.v28i0.4439}]}
       
 Alonso-Ovalle, Luis, and Henrison Hsieh. 2018. Overcoming the Unexpected: The Tagalog Ability/Involuntary Action Form.  \textit{Proceedings of the Thirty-Fifth West Coast Conference on Formal Linguistics}, ed. by Will Bennett, Lindsay Hracs, and Dennis Storoshenko, Somerville, MA: Cascadilla Proceedings Project.      
      
 Alonso-Ovalle, Luis, and Henrison Hsieh. 2017. Causes and Expectations: On the Interpretation of the Tagalog Ability/Involuntary Action Verbal Inflection. \textit{Proceedings of the Twenty-Seventh Semantics and Linguistic Theory Conference}, ed. by Dan Burgdorf, Jacob Collard, Sireemas Maspong, and Brynhildur Stef\'ansd\'ottir, CLC Publications, pp. 75-94. %{\footnotesize [\href{https://doi.org/10.3765/salt.v27i0.4132}{https://doi.org/10.3765/salt.v27i0.4132}]}

Alonso-Ovalle, Luis. 2016. Are All Concessive Scalar Particles the Same? Probing into Spanish \textit{Siquiera}.  \textit{Proceedings of the Twenty-Sixth
  Semantics and Linguistic Theory Conference}, ed. by Mary Moroney and
Carol-Rose Little, CLC Publications, pp. 185-204. %{\footnotesize [\href{https://doi.org/10.3765/salt.v26i0.3820}{https://doi.org/10.3765/salt.v26i0.3820}]}

Alonso-Ovalle, Luis, and Paula Men\'endez-Benito. 2016. Modal Selectivity
in the Nominal Domain: Spanish \textit{Uno Cualquiera}. \textit{Proceedings
of the Forty-Sixth Annual Meeting of the North East Linguistic Society},
ed. by Christopher Hammerly and Brandon Pickett, University of Massachusetts, Amherst, MA: Graduate Linguistics Student Association, pp 1-11.

Alonso-Ovalle, Luis and Junko Shimoyama. 2014. Expressing Ignorance
in the Nominal Domain: Japanese \textit{Wh-ka}. \textit{Proceedings of
  the Thirty-First Annual West Coast Conference on Formal Linguistics}, ed. by Robert
Santana-LaBarge, Somerville, MA: Cascadilla Proceedings Project, pp. 11-20.

Alonso-Ovalle, Luis and Paula
Men\'endez-Benito. 2013. Modal Determiners and Alternatives:
Quantity and Ignorance Effects.  \textit{Proceedings of the Twenty-Third
  Semantics and Linguistic Theory Conference}, ed. by Todd Snider, CLC
Publications, pp. 570-586. %{\footnotesize [\href{https://doi.org/10.3765/salt.v23i0.2671}{https://doi.org/10.3765/salt.v23i0.2671}]}

Alonso-Ovalle, Luis and Paula
Men\'endez-Benito. 2013. Epistemic Indefinites: Are We Ignorant About
Ignorance? \textit{Proceedings of the Nineteenth Amsterdam Colloquium},
ed. by Maria Aloni, Michael Franke and Floris Roelofsen, University of
Amsterdam, pp. 35-43.

Alonso-Ovalle, Luis and Paula
Men\'endez-Benito. 2013. Plural Epistemic
  Indefinites.  \textit{Proceedings of the Fortieth Annual Meeting of the North East Linguistics
    Society}, ed. by Seda Kan, Claire Moore-Cantwell and Robert
  Staubs, University of Massachusetts, Amherst, MA: Graduate Linguistic Student Association, pp. 17-31.

Alonso-Ovalle, Luis and Paula Men\'endez-Benito. 2013. Random
Choice Modality: Spanish \textit{Un {\em NP}
  Cualquiera}. \textit{Proceedings of the Seventeenth Annual} Sinn und Bedeutung \textit{Conference}, ed. by
Emmanuel Chemla, Vincent Homer and Gr\'egoire Winterstein, Paris, pp. 27-43.
% {\footnotesize [\href{http://semanticsarchive.net/sub2012/}{http://semanticsarchive.net/sub2012/}]}

Alonso-Ovalle, Luis and Paula Men\'endez-Benito. 2011. Expressing Indifference: Spanish
\textit{Un {\em NP} Cualquiera}. \textit{Proceedings of the Twenty-First
  Semantics and Linguistic Theory Conference}, ed. by Neil Ashton,
Anca Chereches, and David Lutz, pp. 333-352. 
%{\footnotesize [\href{http://elanguage.net/journals/salt/issue/view/324]}{http://elanguage.net/journals/salt/issue/view/324]]}}

Alonso-Ovalle, Luis; Men\'endez-Benito, Paula, and Schwarz,
Florian. 2011. Maximize Presupposition and Two Types of Definite
Competitors. \textit{Proceedings of the Thirty-Ninth Annual Meeting of the North East Linguistics
  Society}, ed. by Suzi Lima, Kevin Mullin, and Brian
Smith, pp. 29-41. 


Alonso-Ovalle, Luis. 2009. \textsc{Even} and Biased Questions: The Case of Spanish \textit{Siquiera}. \textit{Proceedings of the Nineteenth Semantics and Linguistic Theory Conference}, ed. by Satoshi Ito and Ed Cormany, Cornell University, pp. 1-18.% {\footnotesize [\href{https://doi.org/10.3765/salt.v19i0.2540}{https://doi.org/10.3765/salt.v19i0.2540}]}


Alonso-Ovalle, Luis \textit{\&} Paula
    Men\'endez-Benito. 2008. Minimal Domain Widening. \textit{Proceedings of the Twenty-Seventh
    West Coast Conference on Formal Linguistics,} ed. by Natasha Abner
  and Jason Bishop,  Somerville, MA: Cascadilla Press Project,
  pp. 36-44.


Alonso-Ovalle, Luis. 2008b. Alternatives in the
  Disjunctive Antecedents Problem. \textit{Proceedings of the Twenty-Sixth
    West Coast Conference on Formal Linguistics}, ed. by Charles
  B. Chang and Hannah J. Haynie, Somerville, MA: Cascadilla Press Project, pp. 42-50


Alonso-Ovalle, Luis. 2005. Distributing the Disjuncts over the Modal Space. \textit{Proceedings of the Thirty-Fifth Annual Meeting of the North East Linguistic Society}, ed.\ by Leah Bateman and Cherlon Ussery,  University of Massachusetts, Amherst, MA: Graduate Linguistic Student Association, pp. 75-86. 

Alonso-Ovalle, Luis. 2004. Simplification of Disjunctive Antecedents. \textit{Proceedings of the Thirty-Fourth Annual Meeting of the North East Linguistic Society}, ed.\ by Keir Moulton and Matthew Wolf,  University of Massachusetts, Amherst, MA: Graduate Linguistic Student Association, pp. 1-15.


Alonso-Ovalle, Luis \textit{\&} Elena Guerzoni. 2004. Double Negation, Negative Concord and Metalinguistic Negation. \textit{Proceedings of the Chicago Linguistics Society Meeting, 38-1: The Main Session,} ed. by Mary Andronis, Erin Debenport, Anne Pycha and Keiko Yoshimura. Chicago, IL: Chicago Linguistics Society Publications, pp. 15-31.



Alonso-Ovalle, Luis \textit{\&} Paula Men\'endez-Benito. 2003. Some Epistemic Indefinites. \textit{Proceedings of the Thirty-Third Annual Meeting of the North East Linguistic Society}, ed. by Makoto Kadowaki and Shigeto Kawahara,  University of Massachusetts, Amherst, MA: Graduate Linguistic Student Association, pp. 1-12. 

% \begin{itemize}[ ]
% \item Preprint {\scshape url:} \href{http://www.alonso-ovalle.net/papers/alonso-menendez_NELS2003.pdf}{www.alonso-ovalle.net/papers/alonso-menendez\_NELS2003.pdf}
% \end{itemize}

Alonso-Ovalle, Luis \textit{\&} Paula Men\'endez-Benito. 2002. Two Types of Weak Quantifiers: Evidence from Spanish. \textit{Proceedings of the First North American Summer School in Logic, Language and Information}. Stanford, CA: Department of Linguistics, pp. 1 -19. 

% \begin{itemize}[ ]
% \item Preprint {\scshape url:} \href{http://www.alonso-ovalle.net/papers/alomen.pdf}{www.alonso-ovalle.net/papers/alomen.pdf}
% \end{itemize}

% \end{revnumerate}

\subsection*{Book Reviews}
% \renewcommand{\labelenumi}{{B}\theenumi.}
% \renewcommand{\theenumii}{\roman{\enumii}}
% \begin{revnumerate}
Alonso-Ovalle, Luis. 2008. ``\textit{Fundamentos de sem\'antica composicional.} By Mar\'ia Victoria Escandell Vidal. Barcelona: Ariel, 2004.''  \textit{eLanguage} {\footnotesize \href{http://elanguage.net/blogs/booknotices/?p=17}{http://elanguage.net/blogs/booknotices/?p=17}}

Alonso-Ovalle, Luis. 2002. ``\textit{Definite Descriptions: A Reader.} Ed. by Gary Ostertag. Cambridge: the \textsc{mit} press, 1998.''  \textit{Language}, 78(2), p. 370.

Alonso-Ovalle, Luis. 2002. ``\textit{Speaking of Events.} Ed. by James Higginbotham, Fabio Pianesi and Achille C. Varzi. Oxford: Oxford University Press, 2000.'' \textit{Language,} 78 (2): p. 370.

Alonso-Ovalle, Luis. 2001. ``\textit{The Proceedings of the Seventh West Coast Conference on Formal Linguistics.} Ed. by Shahin \textit{et al}. Stanford: Stanford Linguistics Association, 2001.'' {\it Language,} 77 (2), p. 418.

Alonso-Ovalle, Luis. 2001. ``{\it Pragmatics.} By Jean Stilwell Peccei. London and NY: Routledge, 1999.'' {\it Language,} 77,2, p. 407.

Alonso-Ovalle, Luis. 2001. ``{\it Grammatical Analyses in Basque and Romance Linguistics: Papers in Honor of Mario Saltarelli.} Ed.\ by J. Franco \textit{et al}. Amsterdam: John Benjamins, 1999.'' {\it Language,} 77 (2), p. 407.

Alonso-Ovalle, Luis. 2001. ``{\it Language and Reality: An Introduction to the Philosophy of Language}. By  Michael Devitt and Kim Sterelny. 2nd ed. Cambridge, MA: the \textsc{mit} Press, 1999.'' {\it Language}, 77 (1), p. 188.

Alonso-Ovalle, Luis. 2000. ``{\it Formal Perspectives on Romance Linguistics.} Ed.\ by J.M. Authier \textit{et al}. Amsterdam: John Benjamins, 1999.'' {\it Language}, 76,4, p. 941.
 

%  \section*{Book notices}
%  \renewcommand{\labelenumi}{{B}\theenumi.}
%  \renewcommand{\theenumii}{\roman{\enumii}}
%  \begin{revnumerate}
%  \item \textit{Fundamentos de sem\'antica composicional.} By Mar\'ia Victoria Escandell Vidal. Barcelona: Ariel, 2004. (Submitted to \textit{Language}).
%  \item \textit{Definite Descriptions: A Reader.} Ed. by Gary Ostertag. Cambridge: \textsc{Mit} press, 1998. In \textit{Language}, 78,2, p. 370.

%  \item \textit{Speaking of Events.} Ed. by James Higginbotham, Fabio Pianesi and Achille C. Varzi. Oxford: Oxford University Press, 2000. In \textit{Language,} 78,2, p. 370.

%  \item \textit{The Proceedings of the Seventh West Coast Conference on Formal Linguistics.} Ed. by Shahin \textit{et al}. Stanford: Stanford Linguistics Association, 2001. In {\it Language,} 77,2, p. 418.

%  \item {\it Pragmatics.} By Jean Stilwell Peccei. London and NY: Routledge, 1999. In {\it Language,} 77,2, p. 407.

%  \item {\it Grammatical Analyses in Basque and Romance Linguistics: Papers in Honor of Mario Saltarelli.} Ed. by J. Franco \textit{et al}. Amsterdam: John Benjamins, 1999. In {\it Language,} 77,2, p. 407.

%  \item {\it Language and Reality: An Introduction to the Philosophy of Language}. By  Michael Devitt and Kim Sterelny. 2nd ed. Cambridge, MA: The \textsc{mit} Press, 1999. In {\it Language}, 77,1, p. 188.
%  \item {\it Formal Perspectives on Romance Linguistics.} Ed. by J.M. Authier \textit{et al}. Amsterdam: John Benjamins, 1999. In {\it Language}, 76,4, p. 941.
%  \end{revnumerate}

\subsection*{Edited Volumes}

Alonso-Ovalle, Luis \& Paula Men\'endez-Benito. (eds.) (2015) \emph{Epistemic Indefinites. Exploring Modality beyond the Verbal Domain}, Oxford University Press.

Alonso-Ovalle, Luis. (ed.) 2003. \emph{On Semantic Processing, University of Massachusetts Occasional Papers in Linguistics, vol 27}. University of Massachusetts, Amherst, MA: Graduate Linguistic Student Association.


\subsection*{Invited Talks}

``Singular Bare Interrogatives: a Case for Higher Order Quantification, a Weak Singular and Strong Plural'', (with Vincent Rouillard), S\'eminaire SynSem, Laboratoire de Linguistique, University of Nantes, France, April 1, 2022.

``Random Choice Indefinites: \textit{Uno Cualquiera}'', (with Paula Men\'endez-Benito), invited talk at semantics seminar (LING 879: Modality: Themes and Variations on Force and Flavor), University of Maryland, March 24, 2021.

``Spanish Bare Interrogatives and Number'', (with Vincent Rouillard), SENSUS, Constructing Meaning in Romance, University of Massachusetts, Amherst (online meeting), September 26, 2020.

``Random Choice Modality Beyond Romance: The View from Chuj (Mayan)'', (with Justin Royer), Indefinita in der Romania, XXXVI Romanistentag, University of Kassel, Germany, September 30, 2019.

``Keep \textit{Only} Strong'', (with Aron Hirsch), Department of Linguistics Colloquium, University of Maryland, April 26, 2019.

``Against the Odds. On the Modal Component of the Ability/Involuntary Action Verbal Inflection in Tagalog'', (with Henrison Hsieh), Tenth Toronto-Montr\'eal-Ottawa Semantics Workshop, University of
Toronto, April 22, 2017.

``Epistemic Indefinites, Again'', (with Paula Men\'endez-Benito), Department of English Linguistics, University of G\"{o}ttingen, April 2017 [presented by co-author.]

``Modal Anchors and Modal Indefinites: Spanish \textit{Uno Cualquiera}'', (with Paula Men\'endez-Benito), University of Cologne, Institut f\"ur deutsche Sprache und Literatur, February 2017 [presented by co-author.]

``Modal Selectivity and Modal Harmony: Spanish \textit{Uno Cualquiera}.'' (with Paula Men\'endez-Benito), Logic, Language and Cognition Center, Hebrew University of Jerusalem, May 25 2016, [presented by co-author]

``Modality in the Nominal Domain: Random Choice and Modal Harmony", (with Paula Men\'endez-Benito), Department of Linguistics Colloquium, Cornell University, February 5, 2015.

``Modality in the Nominal Domain: Random Choice'',
(with Paula Men\'endez-Benito), \textit{Two Days At Least Workshop},
University of Utrecht, The Netherlands, September 10 2014.

``Indefinites, Dependent Plurality and Scalar
Alternatives'', (with Paula Men\'endez-Benito), Linguistics Department, Guest lecture series, University of Stuttgart, Germany, January 17 2013. [Presented by co-author]

``Spanish Indefinites and Dependent Plurality: the Role of
Scalarity'',  (with Paula Men\'endez-Benito), \textit{Linguistics colloquium, Zentrum f\"{u}r
  Allgemeine Sprachwissenschaft}, Berlin, June 15 2012. [Presented by co-author.]

``Indiscriminate Choices: Spanish \textit{Uno
  Cualquiera}'', (with Paula Men\'endez-Benito), Fifth Toronto-Montreal-Ottawa Semantics Workshop, University of
Ottawa, March 10 2012.

``Natural language disjunction and the logic of our
minds'', \textit{McGill Canadian Conference for Linguistics
  Undergraduates}, McGill University, March 9, 2012.

``Scalarity and Dependent Plurality in Spanish'', (with Paula Men\'endez-Benito),
Department of Classics, Modern Languages and Linguistics, Concordia
University, February 2 2012.

``Agent Indifference: The Case of Spanish \textit{Un NP
  Cualquiera}'', (with Paula Men\'endez-Benito), School of Linguistics and Language Studies, Carleton
University, Ottawa, December 2011. 

``On the Modal Component of Spanish \textit{Un NP
  Cualquiera}'', (with Paula Men\'endez-Benito), \textit{Indefinites
  and Beyond}, workshop held at the University of G\"{o}ttingen,
Germany, November 18-19, 2011.

``Scalarity and Dependent Plurality in Spanish'',
(with Paula Men\'endez-Benito), \textit{Sinn und Bedeutung} Workshop
on Weak Referentiality, University of Utrecht, September 9 2011.

``F(ake) Questions'', (with Esther Torrego), Seminari del
Centre de Ling\"{u}\'istica Te\`orica, Universidad Aut\'onoma, Barcelona, May 2011. 

``Spanish Plural Indefinites and Dependent Plurality:
the Role of Scalar Alternatives'', (with Paula Men\'endez-Benito),
Workshop on Alternative Semantics, University of Nantes, October 2010 [presented by co-author.]

``Epistemic Effects, Domain Constraints, and Plurality: the Case
of Spanish \textit{Alg\'un}'', (with Paula Men\'endez-Benito),
University of T\"ubingen, January 2010 [presented by co-author.]


``Towards a Typology of Indefinite Noun Phrases: Dissecting Spanish \textit{Alg\'un}'', Linguistics Colloquium Series, Department of Linguistics, University of Michigan, February 2009. 

``Modal Indefinites'' (with Paula Men\'endez-Benito),  Institute for Logic, Language, and Computation, Department of Philosophy, University of
  Amsterdam, May 2008, [presented by co-author]

``Set Forming \textit{Or}'', Department of Linguistics and Germanic, Slavic, Asian and African Languages, Michigan State University, February 2006.

``Alternatives in the Semantics and Pragmatics of Disjunction'', Department of Spanish, French, Italian and Portuguese, University of Illinois at Chicago, January 2006. 

``Can Modals See the Alternatives?''. New York University Polarity Workshop, Department of Linguistics, New York University, March 2005. 

``Disjunction in Modal Space'', Department of Linguistics, University of Connecticut, February 2005. 


``On the Semantics of \textit{O} and \textit{Alg\'un}'', Department of Hispanic Languages and Literature, State University of New York at Stony Brook, January 2005. 
 
``Equal Rights for Every Disjunct! Quantification over Alternatives or Pointwise Context Change'', New York University Syntax/Semantics Lecture Series, Department of Linguistics, New York University, December 2004.


\subsection*{Invited Commentaries}

``Do Scalar Alternatives Provide Enough Truthmakers? (A Note on Santorio, Paolo (2015) Alternatives and Truthmakers in Conditional Semantics')'', Invited commentary delivered at the 90th Annual Meeting of the American Philosophical Association Pacific Division. San Francisco, CA, March 31 2016. 


\subsection*{Conference Presentations}


\subsubsection*{Papers Delivered}

``Weakening is external to \textit{only}'' (with Aron Hirsch), \textit{Thirty-Third Semantics and Linguistic Theory Conference}, Yale University, May 12, 2023.

``Universal Force from Exhaustification:
Farsi \textit{Hame} \textit{-i} DPs'' (with Esmail Moghiseh), \textit{Thirty-Second Semantics and Linguistic Theory Conference}, Colegio de M\'exico, Universidad Nacional Aut\'onoma de M\'exico [virtually], June 9, 2022.

``Sub-Eventive Modal Projection:
The Case of Spanish Subjunctive Relative Clauses'' (with Paula Men\'endez-Benito and Aynat Rubinstein), \textit{Fifty-Second Meeting of the North East Linguistic Society}, Rutgers University [virtually], October 31, 2021.


``Sub-Eventive Modal Projection:
The Case of Spanish Subjunctive Relative Clauses'' (with Paula Men\'endez-Benito and Aynat Rubinstein), \textit{SENSUS 2, Constructing Meaning in Romance}, University of Massachusetts at Amherst [virtually], October 2, 2021.

``Modality in the nominal domain: The Chuj \textit{Yalnhej+wh} Series'' (with Justin Royer), \textit{Thirty-First Semantics and Linguistic Theory Conference}, Brown University [virtually], May 7, 2021.

``Concessive scalar items: Symmetric vs. Non-symmetric Alternatives'' (with Elizabeth Heredia-Murillo), \textit{SENSUS, Constructing Meaning in Romance}, University of Massachusetts at Amherst [virtually], September 27, 2020.

``Random-Choice Modality: The View from Chuj (Mayan)'' (with Justin Royer), \textit{Sinn und Bedeutung 24}, University of Osnabr\"{u}ck, September 5, 2019. [presented by co-author.]

``Neutralizing Free Choice Items via Maximal Domain Restriction: Farsi \textit{-i} Indefinites'' (with Esmail Moghiseh), \textit{Twenty-Ninth Semantics and Linguistic Theory Conference}, University of California at Los Angeles, May 18, 2019.

``Number Inflection, Spanish Bare Interrogatives, and Higher-Order Quantification'' (with Vincent Rouillard), \textit{Going Romance}, University of Utrecht, December 12, 2018 [presented by co-author.]

``Number Inflection, Spanish Bare Interrogatives, and Higher-Order Quantification'' (with Vincent Rouillard), \textit{Forty-Ninth
  Meeting of the North East Linguistic Society}, Cornell University, October 6 2018.

``Contradiction-Free Strengthening and Alternative Discharge: Farsi \textit{i}-Indefinites'' (with Esmail Moghiseh), \textit{Sinn und Bedeutung 23}, Centre de Ling\"{u}\'istica Te\`orica, Universitat Aut\`onoma de Barcelona, September 6, 2018.
 
``Strong \textit{Only}'' (with Aron Hirsch), \textit{Semantics 2018: Looking Ahead}, University of Massachusetts at Amherst, March 10, 2018.
 

``Anchored implicatives: Tagalog Ability/Involuntary Action'' (with Henrison Hsieh), \textit{The Semantics of African, Asian and Austronesian Languages (Triple A 4)}, the University of Gothenburg, Sweden, June 8, 2017 [presented by co-author.]

``Overcoming the Unexpected: The Tagalog Ability/Involuntary Action Form'' (with Henrison Hsieh),  \textit{Thirty-Fifth West Coast Conference on Formal Linguistics}, University of Calgary, April 28, 2017 [presented by co-author.]


``Anchored implicatives: Tagalog Ability/Involuntary Action'' (with Henrison Hsieh), \textit{The Thirty-Fourth meeting of the Austronesian Formal Linguistics}, the University of Washington, April 9, 2017. [presented by co-author.]

``Spanish \textit{Siquiera} in the \textsc{Even} Landscape.", \textit{Chicago Linguistics Society Fifty-Second Annual Meeting}, University of Chicago, April 21, 2016. 

``Puzzling over Epistemic Indefinites, Again." (with Paula
Men\'endez-Benito), \textit{Workshop on Epistemic Modality and Reference}, Universit\'e de Toulouse [presented by co-author.]

``Epistemic Indefinites and Evidential Constraints:
Spanish \textit{Alg\'un}''  (with Paula
Men\'endez-Benito), \textit{Nineteenth Amsterdam Colloquium}, University of Amsterdam,
December 18, 2013.

``Modal Indefinites and Their Competitors: \textit{Alg\'un
  que Otro}'' (with Paula
Men\'endez-Benito), \textit{Congr\'es International des Linguistes 19},
Session on Semantics-Pragmatics Interfaces, Geneva, July 25 2013.

``Indifference and Modality: the Case of Spanish \textit{Uno
Cualquiera}'' (with Paula
Men\'endez-Benito), \textit{Modality Workshop}, University of Ottawa, April 10 2012

``Modality in the Nominal Domain: Exploring Japanese
\textit{Wh-ka} Indeterminates'' (with Junko Shimoyama), \textit{Modality Workshop}, University of Ottawa, April 10 2012

``Epistemic Indefinites: A Personal View'' (with Paula
Men\'endez-Benito), \textit{Workshop on Epistemic Indefinites},
University of G\"{o}ttingen and Lichtenberg-Kolleg, June 2010.

``Epistemic Effects and Plurality'' (with Paula
Men\'endez-Benito), \textit{Workshop on Indefinites
  Crosslinguistically, Thirty-Second Meeting of the German Linguistic Society},
Humboldt University, Berlin, February 2010.

``Modal Indefinites and Domain Constraints'' (with Paula
Men\'endez-Benito), \textit{Workshop on Reference and Discourse
  Structure}, University of Stuttgart, January 2010 [presented by co-author].

``Plural Epistemic Indefinites'' (with Paula Men\'endez-Benito), \textit{Fortieth
  Meeting of the North East Linguistic Society}, M.I.T., October 2009.

``Distributed Plurality in Spanish: \textit{Unos} vs. \textit{Algunos}''  (with Paula Men\'endez-Benito), \textit{Sinn und Bedeutung} 14, University of Vienna, September 2009 [presented by co-author].

``Some Puzzles for Maximize Presupposition'' (with
  Paula Men\'endez-Benito and Florian Schwarz), \textit{M.I.T Workshop in
  Honor of Prof. Angelika Kratzer}, December 2008.

``Minimal Domain Widening'' (with Paula Men\'endez-Benito), \textit{Twenty-Seventh West Coast Conference on
  Formal Linguistics}, University of California Los Angeles, May 2008, 

``Another Look at Indefinites in Islands'' (with Paula
  Men\'endez-Benito), \textit{Workshop on Different Kinds of Specificity
  Across Languages}, Humboldt-Universitat zu Berlin, July 6
  -7, July 2007 [presented by co-author.]

``Alternatives in the Disjunctive Antecedents Problem'', \textit{Twenty-Sixth West Coast Conference on Formal Linguistics}, University of California Berkeley, April 2007.


``Disjunctive Counterfactuals in a Hamblin Semantics'', \textit{Thirty-Third Meeting of the Berkeley Linguistics Society}, University of California Berkeley, February 2007. 

``Identity Preserving \textit{Or}: Disjunction in Alternative Semantics'', \textit{The Linguistic Society of America Summer Institute}, Massachusetts Institute of Technology \& Harvard University, August 2005. 

``Set Forming \textit{Or}'', \textit{The 79th Annual Meeting of the Linguistic Society of America}, San Francisco, January 2005. 

``Equal Rights for Every Disjunct! Quantification over Alternatives or Pointwise Context Change?'', \textit{Sinn und Bedeutung 9}, University of Nijmegen, November 2004. 

``Simplification of Disjunctive Antecedents in a Hamblin Semantics'', \textit{Thirty-Fifth
  Meeting of the North East Linguistic Society}, State University of New York at Stony Brook, November 2003. 

``Two Types of Indefinites'' (with Paula Men\'endez-Benito), \textit{Sinn und Bedeutung} 7, University of Konstanz, October 2002. 

``Two Types of Weak Quantifiers: Evidence from Spanish'' (with Paula Men\'endez-Benito), \textit{First North American Summer School in Language, Logic and Information}, Stanford University, 2002. 

``Spanish \textit{De}-Clauses are not Always on the Right Mood'', \textit{Going Romance 2001}, University of Amsterdam. 

``Is the `Arbitrary Interpretation' a Semantic Epiphenomenon?'', \textit{Going Romance 2000}, Utrecht Institute of Linguistics.

``Situations within Spanish Metaphysics''. \textit{Massachusetts Symposium on Hispanic Linguistics}, University of Massachusetts at Amherst, 2000. 

``On Anaphora Resolution in Spanish: Bound Variable \textit{vs.} Coreferential Reading'' (with Francesco D'Introno and Susana Fern\'andez-Solera), \textit{Fourth Hispanic Linguistics Symposium}, University of Indiana, Bloomington, 2000. 

``Aspect and Situations: On the Semantic Variability of Spanish \textit{Al}-Clauses'', \textit{First International Conference on the Semantics and Pragmatics of Spanish}, The Ohio State University, 1999. 

``Full and Null Pronouns in Spanish: The Zero Pronoun Hypothesis'', \textit{Third Hispanic Linguistics Symposium}, Georgetown University, 1999. 

``Sobre el comportamiento anaf\'orico de los pronombres fuertes en espa\~nol'', \textit{49th Mountain Interstate Foreign Language Conference}, University of Tennessee, 1999. 

``Infinitivos, adjunciones y marcado casual'', \textit{48th Mountain Interstate Foreign Language Conference}, Virginia Tech, Roanoke, VA, 1998. 

``Cuervo en el panorama ling\"{u}\'istico europeo de fin de siglo'', \textit{51st Annual Kentucky Foreign Language Conference}, University of Kentucky, Lexington, KY, 1998. 

\subsubsection*{Poster Presentations}

``Structural ambiguity in pseudo-partitives:
the case of quantity nouns'' (with Bernhard Schwarz), \textit{Thirty-Third Semantics and Linguistic Theory Conference}, Yale University, May 12, 2023.


``Two Types of Intensional Transitive Verbs: The View from Farsi'' (with Esmail Moghiseh), \textit{The Twenty-Third Amsterdam Colloquium}, University of Amsterdam [online presentation], December 20, 2022.

``Against Wide Scope \textit{Any}'' (with Esmail Moghiseh and Jonathan Palucci), \textit{Thirty-Ninth Annual West Coast Conference on Formal Linguistics}, University of Arizona [online meeting], April 9, 2021.

``Concessive Scalar Items: More about \textit{Siquiera} in Spanish'' (with Elizabeth Heredia-Murillo),
\textit{Going Romance 34}, Paris-8 \& CNRS, November 26, 2020 [Flash talk, virtual meeting]

``Numeral
\textit{Any}: In Favor of Viability'' (with Jonathan Palucci),  \textit{Fifty-First Meeting of the
  North East Linguistic Society}, Universit\'e de Qu\'ebec \`a
Montr\'eal, November 6, 2020 [Flash talk, virtual meeting.]

``Numeral \textit{Any}: the View from Farsi'' (with Esmail Mogiseh), \textit{Thirtieth Semantics and Linguistic Theory Conference}, Cornell University, August 2020, [virtual meeting.]

``Neutralizing Free Choice items via domain restriction: Farsi \textit{-i} indefinites'', (with Esmail Mogiseh), \textit{Twelfth Toronto-Ottawa-Montreal Workshop in Semantics}, March 30, 2019, Concordia University, Montreal.

``La expresi\'on de la modalidad de decisi\'on arbitraria en Chuj'' (with Justin Royer), \textit{Form and Analysis in Mayan Linguistics 5}, August 10-11, 2018, Antigua. Guatemala, Centro de Formaci\'on de la Cooperaci\'on Espa\~nola en Antigua, Guatemala [presented by co-author.]

``Keep \textit{Only} Strong'' (with Aron Hirsch), \textit{Twenty-Eighth Semantics and Linguistic Theory Conference}, M.I.T., May 2018. 

``Causes and Expectations: On the Interpretation of the Tagalog Ability/Involuntary Action Verbal Inflection'' (with Henrison Hsieh), \textit{Twenty-Seventh Semantics and Linguistic Theory Conference}, University of Maryland, May 2017. 


``Are All Concessive Scalar Particles the Same? Probing into Spanish \textit{Siquiera}'', \textit{Semantics and Linguistic Theory 26}, University of Texas Austin, May 2016. 

``Modal Selectivity in the Nominal Domain: Spanish \textit{Uno Cualquiera}'' (with Paula Men\'endez-Benito), \textit{46th Meeting of the North East Linguistic Society}, Concordia University, Montreal, October 2015. 

``Modal Determiners and Alternatives: Quantity and Ignorance
Effects'' (with Paula Men\'endez-Benito), \textit{Semantics and
  Linguistic Theory 23}, University of California Santa Cruz, May 2013. 

``Expressing Random
Choice: the Case of Spanish \textit{Uno Cualquiera}''  (with Paula Men\'endez-Benito), \textit{Sinn
  und Bedeutung 17}, \'{E}cole Normale Sup\'{e}rieure, Paris, September 2012.

``Expressing Indifference: Spanish \textit{Un NP
  Cualquiera}'' (with Paula Men\'endez-Benito), \textit{Semantics and
Linguistic Theory 20}, Rutgers University, May 2011. 

``\textsc{Even} and Biased Questions: the Case of Spanish \textit{Siquiera}'', \textit{Semantics and Linguistic Theory 19}, the Ohio State University, April 2009. 

``Maximize Presupposition and Definite Competitors'' (with
  Paula Men\'endez-Benito and Florian Schwarz), \textit{39th
  Meeting of the North East Linguistic Society}, Cornell University, November 2008. 


``Exceptional Scope Across Islands'' (with Paula Men\'endez-Benito, \textit{27th West Coast Conference on
  Formal Linguistics}, University of California Los Angeles, May 2008. 


``A (Kratzer and Shimoyama Style) Hamblin Semantics for Disjunction'', \textit{35th
  Meeting of the North East Linguistic Society}, University of Connecticut, Storrs, November 2004. 


``A Negative Concord Exceptive: Japanese \textit{-sika}'' (with Masako Hirotani), \textit{35th
  Meeting of the North East Linguistic Society}, University of Connecticut, Storrs, November 2004. 


``Incremental Modification of Discourse Referents: the Case of Restricted Quantification'', \textit{16th Annual City University of New York Conference on Sentence Processing}, Massachusetts Institute of Technology, March 2003. 

``Indefinites and Quantification: the Case of Spanish'', (with Paula Men\'endez-Benito),\textit{33rd
  Meeting of the North East Linguistic Society} , Massachusetts Institute of Technology,  November 2002. 

``Double Negation, Metalinguistic Negation and Negative
Concord'' (with Elena Guerzoni), \textit{37th Meeting of the Chicago
  Linguistics Society}, University of Chicago, April 2001. 

\section*{Teaching}

\subsection*{McGill University (2011-)}

\subsubsection*{Undergraduate level}

\textsc{Ling} 200: Introduction to the Study of Language (Fall 2015.)

\textsc{Ling} 201: Introduction to Linguistics (Semantics and Pragmatics
section), (Winter 2013.)

\textsc{Ling} 260: Meaning in Language (Fall 2017, Fall 2019, Fall 2021.)

\textsc{Ling} 565: Pragmatics (Winter 2017, Winter 2019.)

\textsc{Hisp} 199 (First Year Seminar): Varieties of Spanish (Winter 2012.)

\textsc{Hisp} 310: How Spanish Works (Fall 2012, Fall 2013, Fall 2014.)

\textsc{Hisp} 380: Global Spanish (Winter 2014.)

\textsc{Hisp} 501: History of the Spanish Language (Fall 2011; Fall 2015 (taught as \textsc{Hisp} 505, Seminar in Hispanic Studies.))



\subsubsection*{Graduate level}

\textsc{Ling} 665: Semantics 4 (Winter 2012, Winter 2014, Winter 2018, Winter 2020, Winter 2022 (meets together with
Ling 765).)

\textsc{Ling} 660: Semantics 3 (Fall 2012, Fall 2014, Fall 2016, Fall 2018, Fall 2020.)

LLCU 610: Fundamentals of Linguistics for Language Teaching (Winter 2013.)


\subsection*{Doctoral Students}


\subsubsection*{PhD Dissertations}


\subsubsection*{Completed}

Brian Buccola, ``Maximality in the Semantics of Modified Numerals", (co-supervised with Bernhard Schwarz, successfully defended in August 2015.)

Francesco Gentile, ``Non-Local Modification'', (co-supervised with Bernhard Schwarz and Junko Shimoyama, successfully defended on December 9, 2019.)

Dan Goodhue, ``On Asking and Answering Biased Polar Questions", (co-supervised with Bernhard Schwarz and Michael Wagner, successfully defended in February 2018.)

Jozina van der Klok, ``Tense and Aspect Markers in Javanese'',
(co-supervised with Lisa Travis, successfully defended in November
2012.)


Mathieu Paill\'e, ``Local Exh'', (co-supervised with Bernhard Schwarz, successfully defended in August 2022, K. B. Jenkes Prize, Graduate and Postdoctoral Studies, McGill University.)

Justin Royer, ``Elements of (In)definiteness and Binding: A Mayan Perspective'', (co-supervised with Jessica Coon and Aron Hirsch, successfully defended in June
2022, Arts Dissertation Award in the Humanities/ Social Sciences.)

\vspace{-10pt}

\subsubsection*{In progress}

William Johnston, ``Serial Verb Constructions in Hmong,'' (co-supervised with Jessica Coon, in progress.) 

Esmail Moghiseh, ``Free Choice in Farsi'', (in progress)

\vspace{-10pt}

\subsubsection*{Committee Member}

Elizabeth Heredia-Murillo, University of Nantes / University of Gr\"{o}ningen.

Alanah McKillen, ``On the interpretation of reflexive pronouns'', (succesfully defended in March 2016).

Tokiko Okuma, ``Overt Pronoun Constraint Effects in Second Language Japanese'', (successfully defended in April 2015.)

Alexandra Simonenko, ``Grammatical Ingredients of Definiteness'',
(successfully defended in April 2014.)
\vspace{-10pt}


\subsubsection*{Evaluation Papers}

\subsubsection*{(Co-)Supervisor}

\subsubsection*{Completed}


Amy Bruno, ``Contrastive negation and Presuppositional Alternatives'', (co-supervised with Bernhard Schwarz, successfully defended in May 2017.)

Francesco Gentile, ``Adjectives as Reduced Relative Clauses?
The case of Italian Prenominal and Postnominal adjectives.'', (successfully defended in April  2017.)

Dan Goodhue, ``On the Presuppositions of Epistemic \textit{Must}", (co-supervised with Bernhard Schwarz, successfully defended in March 2015.)

Henrison Hsieh, ``An Additional Inference for Actuality Entailments'',
(co-supervised with Bernhard Schwarz, successfully defended in June 2015.)

Will Johnston, ``Questions and Cumulative Readings'', (co-supervised with Bernhard Schwarz, succesfully defended in May 2020).

Will Johnston, ``\textit{Again} and Intensional Transitive Verbs'', (co-supervised with Junko Shimoyama, succesfully defended in February 2021).

Oriana Kilbourn-Cer\'on, ``\textit{Almost}'', (co-supervised with Bernhard Schwarz,
successfully defended in August 2013.) 

Gretchen McCulloch, ``Modal Indefinites in Mi'gmaq: \textit{Tampas}'', (defended in July 2013.)

Alanah McKillen, ``Focus and Binding'' (co-supervised with Yosef
Grodzinsky, successfully defended in August 2013.)

Dejan Milacic, ``Irrealis Mood in Kabyle'' (defended in summer 2017.)

Esmail Moghiseh, ``Uniqueness and Existential Free Choice Items in Farsi" (successfully defended in July 2020).

Marzieh Mortazavinia, ``\textit{Even} and \textit{Only}''
(co-supervised with Bernhard Schwarz, successfully defended in July
2013. )

Mathieu Paill\'e, ``Term Colors and Exhaustive Readings.'' (co-supervised with Bernhard Schwarz, successfully defended in June 2020)

Jonathan Palucci, ``On the Scope Effects of \textit{Any}.'', (successfully defended in May 2021).

Jonathan Palucci, ``Modal Ingredients of \textit{Have}: Disentangling Causers from Engineers'' (eval 2, co-supervised with Jessica Coon, successfully defended on April 7, 2022).


%\subsubsection*{In Progress}



\subsubsection*{Committee Member}


Francesco Gentile,  ``Adjectives as reduced relative clauses. The case of Italian prenominal and postnominal adjectives.'' (Co-supervised with Junko Shimoyama, successfully defended in June 2017.)

Daniel Goodhue, ``The Contradiction Contour and Questions''
(Co-supervised with Michael Wagner and Bernhard Schwarz, successfully
defended in May 2014).

\subsubsection*{External Examiner}

Jumanah Abusulaiman, “Modality in Makkan Arabic: The Interaction between Modals and Aspect” University of Ottawa , Ph. D. dissertation, on November 4, 2019.

Ph.\ D evaluation paper examiner: Brandon J. Fry, ``The semantics of attitude ascription: a literature review and a proposal for a study of Ojibwe cross-clausal agreement'', University of Ottawa.

Jared Kabbara, School of Computer Science, dissertation proposal defence, Dec 6. 2019.


\subsection*{Postdoctoral Supervision}

Aron Hirsch, September 2017 -- May 2019 , SSHRC postdoctoral fellow (co-supervised with Bernhard Schwarz and Michael Wagner.)

\subsection*{MA Research Papers}

\subsubsection*{Supervisor}

Esmail Moghiseh, ``Free Choice Items in Farsi'' (fast-tracked to Ph.D. program.)

Jonathan Palucci, ``On the Scope of \textit{Any}'' (fast-tracked to Ph.D. program.)

\subsubsection*{Co-Supervisor}

Jason Borga, ``Topics on sluicing'', (Co-supervised with Aron Hirsch and Bernhard Schwarz.)

\subsection*{Undergraduate Honors Theses (Supervisor)}

Han Yao, 2023. ``Mandarin Chinese m\u{o}u indefinites'' (Cognitive Science Program) (co-supervised with Bernhard Schwarz)

Danielle Celone, 2021. ``The \textit{n'importe qu-} series." 

Esmail Moghiseh, 2018. ``Contradiction free strengthening and exhaustification: Persian -\textit{i} indefinites''.

Erica Brandao, ``Brazilian Portuguese \textit{Algum}.'' (ARIA award, summer 2019) (not completed.)



 

\subsection*{University of Massachusetts Boston (2006-2011)}


Span 412: Spanish Semantics (Fall 2008, Fall 2010).

Span 316: Advanced Grammar (Spring 2007, Spring 2009).

Span 320: Varieties of Spanish in the Americas (Fall 2009).

Span 314: Language Arts: How Spanish Works (Fall 2007, Fall 2009,
Spring 2011).

Span 305: Problems of Syntax (Spring 2007, Spring 2008).

Span 304: Spanish for Majors and Minors (Fall 2006, Fall 2008).

Span 200\textsc{g} (General Education: Intermediate Seminar): Boston
Speaks, one section (Spring 2007, Fall 2010).

Span 202: Intermediate Spanish II  (Fall 2007, Spring 2007, Fall
2009).

Span 102: Elementary Spanish II,  three sections (Fall 2006, Spring
2007).

Span 101: Elementary Spanish I, one section (Fall 2007).	

 \subsubsection*{Honor Theses Directed at UMass Boston}

 Melodie Reynolds, ``Negative Concord and
Spanish Yes/No Questions with Preposed Negation'', (two semesters (6
credits), successfully deffended Spring 2011).

 Katherina Zhovna's (Departmental Honor
  Thesis.)  ``Spanish Epistemic Indefinites: Expressing
  Degrees of Ignorance'', (two semesters (6 credits), successfully defended Summer 2009).

 Patrick Brand, ``Division of
  Labor in the Resolution of Anaphora in Spanish''  (two semesters (6 credits), successfully
  defended Spring 2008).



% \section*{\texbf{\large{External}}}

% \begin{itemize}
% \item 2007. External Member of Aaron Braver's Senior Honor Thesis (``An Account of N-Drop. Empirical Evidence and Analysis''), Brandeis University.
% \end{itemize}

\subsection*{ M.I.T (Fall 2005)}

\textsc{24.970}, Introduction to Semantics, with Prof.\ Kai von
Fintel. Level: graduate. Duties also include teaching and developing
the semantics section of 24.992, Survey of General Linguistics
(graduate level).

\subsection*{University of Massachusetts Amherst (1997-- 2006)}

\subsubsection*{Department of Linguistics}

\textsc{Ling 510:} Introduction to Semantics. Spring 2004. Level:
senior-level undergraduate course. Teaching Assistant to Prof.\
Angelika Kratzer. Duties included preparing and teaching a weekly 50 min. hands-on session, supervising students and grading.

\textsc{Ling 409:} Formal foundations of Linguistics. Fall
2003. Level: senior-level undergraduate course. Teaching Assistant to
Prof.\ Barbara H. Partee. Duties included grading, preparing and teaching several sections of the course. 

\subsubsection*{Department of Spanish and Portuguese}

\textsc{span 470}: Introduction to Hispanic Linguistics.

\textsc{span 378}: Spanish Phonetics. 

\textsc{span 311}: Advanced Grammar. 

\textsc{span 240}: Spanish for General Purposes, Advanced Intermediate level.

\textsc{span 120}:  Spanish for General Purposes, Beginners.

 \textsc{span 110}: Spanish for General Purposes, Beginners.


 Coordinator of the Advanced Intermediate Level Language Program (1998
 -- 2000.) Duties included coordinating Teaching Associates in charge
 of \textsc{span} 240 (Spanish for General Purposes, Advanced
 Intermediate level), designing full structure of the course,
 including syllabus, teaching materials and evaluation of students.

\subsection*{\textbf{Other}}

29-31 March, 2022, six-hour workshop on intensional semantics, Laboratoire de Linguistique, University of Nantes. 

Fall 1999, Teaching Assistant, Spanish Department, Amherst College.

Summer 1996,  Institute for the Cooperation with Latin America Fellow,  Spanish Foreign Office. Duties included teaching two seminars on Structuralist Approaches to the Syntax of Spanish at the National University, C\'ordoba (Argentina).


\subsection*{Talks on Teaching}


2007. ``Enhancing Communication with Voice and Video Chat'' (with Susan Mraz), \textit{Educational Technology Conference}, University of Massachusetts Boston.

2007. ``Bringing Formal Linguistics into the Language Classroom'', \textit{Annual Conference on Teaching for Transformation, Center for the Improvement of Teaching}, University of Massachusetts Boston.

1999. ``Ciencias, t\'ecnicas y tecnolog\'ias: acerca del lugar de la gram\'atica en el paradigma comunicativo'', \textit{52nd Kentucky Foreign Language Conference}, University of Kentucky, Lexington, KY.

\section*{Service}

\subsection*{McGill University (2011 -)}

\subsubsection*{Service to the University}

Strategic Planning Committee, Faculty of Arts (Fall 2018 - )

Tomlinson Postdoctoral Fellowships Selection Commitee, \textit{Graduate and
  Postdoctoral Studies} (Academic Year 2011-2012, Academic Year 2012-2013.)
%(February 5, 2013; January 26, 2012.)

Distinguished Dissertation Award Commitee, \textit{Graduate and
  Postdoctoral Studies}, (2012, 2013, 2014)
%(March 26, 2013; March 27, 2012.)

Convocation Awards Committee, \textit{Graduate and
  Postdoctoral Studies}, (2012, 2013, 2014, 2015)

CGS Master's Scholarships Evaluation Committee, \textit{Graduate and
  Postdoctoral Studies}, (2012, 2013, 2015)
%(May 1st, 2012; May 13, 2013.)

Served as a pro-dean in the following dissertation defenses:

\begin{itemize}
\item Kate E. Rath-Wilson, Department of Neuroscience, July 6, 2015.
\item Christopher Mount, Department of Integrated Studies in
  Education, December 6, 2012.
\item Xiangyu Guo, Department of Chemistry, June 19 2012.
\item Jackson Earle Tulonen Smith, Department of Physiology, May 29 2012.
\item John Mills, Department of Biochemistry, Dec 9 2011.

\end{itemize}

\subsubsection*{Service to the Department}

\subsubsection*{Department of Linguistics}

Chair, August 2016 --

Graduate Program Director (\textit{interim}, Academic Year 2012-2013, Fall 2014)

%Fall 2012 -- Summer 2013).

Co-organizer of the Linguistics Speaker Series (Academic Year 2012-2013.)

% (Summer 2012 -- Summer 2013).

Admissions Committee (annual).

Departmental Tenure and Promotion Committee (2015, Chair 2016 --).

Job Search Committee (2015, 2016).

Co-organizer of the 6th Toronto-Ottawa-Montr\'eal Workshop on
Semantics.

Co-organizer of \textit{Exploring the Interfaces 2: Implicatures,
  Alternatives, and the Semantics/Pragmatics Interface}, a three day
international workshop, funded by SSHRC.

Chair Selection Committee (Winter 2013.)

%(March 2013)

Student Awards Committee (Academic Year 2011-2012, Academic Year
2012-2013 (chair).)

% (May 2nd, 2012; May 1st 2013, chair.)

Full Professor Promotion Guidelines Committee (Winter 2012.)

%(February 6th, 2012).

Merit Criteria Review Committee (since Fall 2012, ongoing.)

Web Committee  (since Fall 2011, ongoing.)

Editor of \textit{McLing}, the departmental newsletter (Fall 2011 --
.)

Internal examiner:  Tokiko Okuma, ``Overt Pronoun Constraint Effects in Second Language Japanese'', Ph. D. dissertation. (Also oral defense committee member: April 1 2015.)

Internal examiner:  David-\'Etienne Bouchard, ``Long-Distance Degree Quantification and the
Grammar of Subjectivity'', Ph. D. dissertation, oral defense: November
24 2012.

Internal examiner:  Alexandra Simonenko, ``The Grammatical Ingredients
of Definiteness'', Ph. D. dissertation, oral defense: April 4 2014.

Oral Defense Committee member: Mina Sugimura, ``Domain Extension:  A Study of Restructuring
Predicates in Japanese and the Role of Head Movement.''
Ph.D. dissertation, Winter 2012. 

Oral Defense Committee member:   Alexandra Simonenko, ``The Grammatical Ingredients
of Definiteness'', Ph. D. dissertation, April 4 2014.

Oral Defense Committee member:  Walter Pedersen, ``Inchoative Verbs and Adverbial Modification: Decompositional and Scalar Approaches'', Ph.D. dissertation, September 05 2014.

Oral Defense Committee member:  Tokiko Okuma,``Overt Pronoun Constraint Effects in Second Language Japanese'', Ph. D. dissertation, oral defense: April 1 2015.

Oral Defense Committee member: Sepideh Mortazavinia, ``Second Language Acquisition of Focus-Sensitive Presupposition Triggers in English and Persian'',  Ph. D. dissertation, oral defense: June 1 2018.


\vspace{-10pt}

\subsubsection*{Department of Languages, Literatures and Cultures}

 Admissions (annual).

Job Search Committee, Faculty Lecturer, Italian, Winter 2012.
%May 2012.


\subsection*{University of Massachusetts Boston (2006-2011)}

\subsubsection*{Service to the University}

Spring 2010. Faculty Development Implementation Committee.

Spring 2009. Faculty Development Committee.

Fall 2009 -- Spring 2010. Seminar Assessment Committee.

Spring 2009. Intermediate Seminar Portfolio Review, Seminar Assessment Committee.
% \item[Spring 2007.] Taught General Education Second Year Seminar: Span 200\textsc{G} Boston Speaks.

Spring 2007, Winter 2008, Spring 2008, Winter 2009. Writing Proficiency Requirement Grader.


\subsubsection*{Service to the College of Liberal Arts}

Fall 2007 -- Spring 2009. College of Liberal Arts Senate.

Fall 2008 -- Spring 2009. College of Liberal Arts Senate Executive Committee.

\subsubsection*{Service to the Department}

Fall 2008.  Department Personnel Committee.

Fall 2006, Fall 2007, Fall 2008. Co-organization of department's
career orientation meetings.

Departmental webmaster.

\subsection*{Service to the Profession}

\subsubsection*{Editorship}

Editor:

\begin{itemize}

\item[] \textit{Language and Linguistics Compass}, Semantics and Pragmatics Section, (2016 --)

\end{itemize}

Editorial board member: 

\begin{itemize}
  \item[] \textit{Semantics and Pragmatics} (2011 -- )
  \item[] \textit{Journal of Semantics} (2015 -- )
  \item[] \textit{Probus. An International Journal of Romance Linguistics} (2016 --)
\end{itemize}

\vspace{-10pt}

\subsubsection*{Reviewing}

Ad-hoc reviewer for articles in the following journals:

Semantics: 

\begin{itemize}
\item[] \textit{Journal of Semantics} (2007 --)
\item[] \textit{Linguistics and Philosophy} (2011 --)
\item[]\textit{Natural Language Semantics} (2006 --) 
\item[] \textit{Semantics and Pragmatics} (2011 --)
\end{itemize}

General:
\begin{itemize}
\item[] \textit{Glossa} (Academic Year 2019-20: 1 manuscript.)
\item[] \textit{Journal of Pragmatics} (Academic Year
  2013-2014: 1
  manuscript.)
  \item[] \textit{Journal of Greek Linguistics} (Academic Year
    2019-2020: 1
    manuscript.)
\item[] \textit{Language} (Academic Year  2009-2010: 1 manuscript.)
\item[] \textit{Linguistic Inquiry} (Academic Year  2004-2005: 1 manuscript. 2019-2020: 1 manuscript.)
\item[] \textit{Lingua} (Academic Year  2012-2013: 1 manuscript.)
\item[] \textit{Natural Language and Linguistic Theory} (Academic Year
  2011-2012: 1
  manuscript.)
  \item[] \textit{Probus} (Academic Year 2017-18: 1 manuscript, AY 2018-19: 1 manuscript, AY 2019-20: 1 manuscript.)
  \item[] \textit{Theoretical Linguistics} (Academic Year 2019-2020:1 manuscript.)
\item[] \textit{Studies in Hispanic and Lusophone Linguistics.} (Academic Year 
  2008-2009: 1 manuscript.)
\item[] \textit{Written Language and Literacy} (John Benjamins) (Academic Year 
  2009-2010: 1 manuscript.)
\end{itemize}


Book manuscripts: Oxford University Press
(Summer 2011: one book manuscript)

Book proposal reviewer for Wiley-Blackwell (Fall 2009: two book
proposals; Spring 2010: one book
proposal; Spring 2011: one book proposal; Winter 2012: one book
proposal; Fall 2012: one book proposal; Fall 2015: one book proposal; Winter 2016: one book proposal), Oxford University Press (Fall 2020: one book proposal), Cambridge University Press (Winter 2023: one book proposal.)

Reviewer for the Real Academia Espa\~nola (chapters 19 and 20 of the \textit{Nueva gramática de la lengua española} April, 2021.)

Reviewed section manuscripts for edited volumes: 
\begin{itemize}
\item[] \textit{Wiley Blackwell Semantics Companion}, Wiley-Blackwell, edited by Lisa Matthewson \textit{et al.}
\item[] \textit{Handbook on Information Structure} (ed. by Caroline F\'try and Shin Ishihare) (1 section, 2014).
\item[] \textit{Modality across Syntactic Categories} (ed. by Mar\'ia Luisa Rivero, Ana Arregui and Andr\'es Salanova), 1 section.
\item[] \textit{Alternatives in Semantics} (ed. by Anamaria Falaus) (2
  sections, 2011).
  \item [] Edited volume on the use of alternatives in semantics (ed. by Daniel Althuser) (1 chapter, 2020.)
\item[] \textit{Proceedings of the 41th Linguistic Symposium on
    Romance Languages} (ed. by Eric Mathieu \textit{et al.}, 1
  section, 2011).
\end{itemize}


Abstract reviewer for conferences:

\begin{itemize}
\item [] \textit{Amsterdam Colloquium} (2012, 2013, 2015, 2017, 2019)
\item[] Canadian Linguistics Association Meeting Program Committee member (2014 -- 2015, 2019, 2020, 2021, 2022)
\item[] \textit{Generative Linguistics in the Old World} (2012, 2014, 2017)
\item[] \textit{Incontro di Grammatica Generativa} (2021)
\item[] \textit{32nd Linguistic Symposium on Romance Languages}, University of Toronto.
\item[] \textit{North East Linguistics Society} (2009 -- )
\item[] \textit{Semantics and Linguistic Theory} (2007 --)
\item[] Seoul International Conference on Generative Grammar (2021)
\item[] \textsc{sensus}, University of Massachusetts at Amherst (2020, 2021).
\item[] \textit{Sinn und Bedeutung} (2009 -- ).
\item[] \textit{West Coast Conference on Formal Linguistics} (2012 -- )
\end{itemize}


Reviewer for funding agencies:

\begin{itemize}
  \item[] Deutsche Forschungsgemeinschaft (DFG) (one grant proposal, 2020)
  \item[] Israel Science Foundation (one grant proposal, 2016)
  \item[] Leibniz Association (Germany) (one grant proposal, 2017)
  \item[] National Science Foundation (one proposal, 2011)
  \item[] Pontificia Universidad Cat\'olica del Per\'u (internal grants, one grant proposal 2016)
  \item[] Social Sciences and Humanities Research Council (one grant proposal, 2020)
  \end{itemize}


External examiner, pre-tenure formal review, Department of Linguistics, the University of Utah.

Tenure case reviewer, CUNY graduate center (2021).

Promotion to full professor reviewer, Concordia University (2021).


\subsection*{Outreach}


September 25 2010: ``Variedades del espa\~nol americano''. Eight-hour
workshop for high school teachers on the varieties of Spanish spoken in America, organized by the
Spanish Resource Center (Spanish Consulate, Boston), University of Massachusetts Boston.

June 13 2009: ``Lo que los libros de texto no te cuentan''. Eight-hour
workshop  on Spanish grammar for high shool teachers organized by the
Spanish Resource Center (Spanish Consulate, Boston), University of
Massachusetts Boston.

Participated in the organization of the 2012 and 2013 editions of the North
American Computational Linguistics Olympiad (NACLO) at McGill.


\subsection*{Honors and Awards} 

University Fellowship, University of Massachusetts, Amherst (Fall
 2004 -- Spring 2005).

University Fellowship, University of Massachusetts, Amherst (Fall 2000
-- Spring 2001).

Certificate of Appreciation for Excellence in Teaching (Division of
Continuing Education, University of Massachusetts, Amherst.) (Awarded
in 1999).

Certificate of Appreciation for Excellence in Teaching (Division of
Continuing Education, University of Massachusetts, Amherst.) (Awarded
in 1998).

`Clar\'in Award' (class 1992). (Awarded in 1997) (highest grade average among majors in Classics, Modern Languages and Philology).


% \section*{References}

% \begin{tabular}{l}
% Prof. Angelika Kratzer \\
% Department of Linguistics\\
% 226 South College\\
% University of Massachusetts, Amherst.\\
% Amherst, MA 01003-7130\\
% \href{mailto: kratzer@linguist.umass.edu}{kratzer@linguist.umass.edu}\\
% \\
% % \begin{tabular}{l}
% % Prof. Kai von Fintel \\
% % Department of Linguistics \textit{\&} Philosophy\\
% % Massachusetts Institute of Technology\\
% % 77 Massachusetts Avenue, 32---D808\\
% % Cambridge, MA 02139-4307\\
% % \href{mailto: fintel@mit.edu}{fintel@mit.edu}\\
% % \end{tabular}
% % \\
% % &\\
% % &\\
% %\begin{tabular}{l}
% Prof. Lyn Frazier\\
% Department of Linguistics\\
% 226 South College\\
% University of Massachusetts, Amherst.\\
% Amherst, MA 01003-7130\\
% \href{mailto: lyn@linguist.umass.edu}{lyn@linguist.umass.edu}\\
% %\end{tabular}
% \\
% %\begin{tabular}{l}
% Prof. Barbara H. Partee\\
% Department of Linguistics\\
% 226 South College\\
% University of Massachusetts, Amherst.\\
% Amherst, MA 01003-7130\\
% \href{mailto: partee@linguist.umass.edu}{partee@linguist.umass.edu}\\
% %\end{tabular} \\
% %\begin{tabular}{l}
% \\
% Prof. Christopher Potts\\
% Department of Linguistics\\
% 226 South College\\
% University of Massachusetts, Amherst.\\
% Amherst, MA 01003-7130\\
% \href{mailto: partee@linguist.umass.edu}{partee@linguist.umass.edu}\\
% \end{tabular}



%{\hspace*{\fill}\footnotesize Updated: \today}


\end{document} 
